The impact of cosmic variance on simulating weak lensing surveys

### 2014-09-22 Writeup/paper_v3.tex
Functional forms for z-dist corrected
Upper limit of z changed to 1.0 from 1.2

Photometric redshifts were determined by~\cite{COSMOS_Photoz_30band}.The accuracy of photometric redshifts for $m_\text{F814W}\le$ 22.5 is $\sigma_{\Delta z} = 0.007(1+z_s)$ and at fainter magnitudes, i.e. $m_\text{F814W}\le$ 24, $\sigma_{\Delta z} = 0.012(1+z_s)$.
The photometric redshift values become noisy beyond $z$ of $1$ for our purposes and the various fits to the galaxies are also not very reliable beyond the apparent magnitude $(m)$ value of 23.5. 
Thus, we will exclude all galaxies that have F814W magnitude greater than 23.5. However, we will use $m_\text{F814W}\le 25.2$ sample in volume-limiting process (cf.~\S\ref{sub:volumelimiting}) to calculate completeness.  We take the $z<1.2$ flux-limited sample to fit redshift distribution models (cf.~\S\ref{sub:overdensities}) and then restrict ourselves to $z\le1$ sample for all further analysis.
% ($S/N \sim 50$ {\bf ?} )
% \rachel{Our catalog has the more up-to-date Ilbert et al. photo-$z$,
%   not the older Mobasher ones.  Need to fix citations. Also, we care
%   about the photo-$z$ accuracy beyond 22.5, so it's important to give
%   some information about it to the depth that we actually use.  Finally, I
%   recommend against mentioning the $S/N$ because the calculation is
%   complicated by the correlated noise, so most people use use
%   magnitude instead of $S/N$.}

@@

%\rachel{I thought we were only going up to $z=0.85$ but here you say $1$?}
%For our sample of galaxies, volume-limited upto $z=1$ by imposing an $M_I$ cut, we fit parametric models to the histogram of photometric redshifts in order to assign values of overdensity. The figures show chi-squared and gamma functions fitted to the histogram~\citep{Redshift_modelling}.
For our (flux-limited) sample of galaxies, up to $z=1.2$, we fit parametric models to the histogram of photometric redshift in order to assign values of overdensity. Figures show Chi-squared distribution given by
\begin{equation}
 p_1(z) = cz^{a-1}\exp({-bz})
\end{equation}
and the function given by
\begin{equation}
 p_2(z) = az^2\exp{(-bz^{1.5})}
\end{equation}
that was first presented by~\cite{Redshift_modelling} as fits to the
redshift histograms. \rachel{(To avoid ambiguity, you should use avoid
  using the same symbol in both equations.  For example you could turn
  the $b$'s into $b_1$ and $b_2$.  Also, the normalization factors out
  front do not matter - they are not something that you fit for.  I
  would say $p(z)\propto$\dots to avoid 
  the need for a normalization for which you are not actually fitting.)} Here $a,b$ and $c$ are free parameters that are to be determined.
%\rachel{You cannot expect people to look these up.  Give them equations in which you define $p(z)$ for each case, with labels like $p_1(z)$ and $p_2(z)$.}
For low $z$, the volume is too small to rely the overdensity values from our model fits and hence the fit is made for $z \ge 0.3$. Our binning width, $\Delta z$ must be small enough so as to be able to identify localized overdensities/underdensities but large enough to not let our conclusions be affected by the errors in photometric redshift. 
We choose our bins to be $0.05$ wide starting from $z=0.3$. 
%\rachel{Were you going to use other fitting functions as a test of the method?  If so, you should introduce them here.}

>>>>

Photometric redshifts were determined by~\cite{COSMOS_Photoz_30band}.The accuracy of photometric redshifts for $m_\text{F814W}\le$ 22.5 is $\sigma_{\Delta z} = 0.007(1+z_s)$ and at fainter magnitudes, i.e. $m_\text{F814W}\le$ 24, $\sigma_{\Delta z} = 0.012(1+z_s)$.
The photometric redshift values become noisy beyond $z$ of $1$ for our purposes and the various fits to the galaxies are also not very reliable beyond the apparent magnitude $(m)$ value of 23.5. 
Thus, we will exclude all galaxies that have F814W magnitude greater than 23.5. However, we will use $m_\text{F814W}\le 25.2$ sample in volume-limiting process (cf.~\S\ref{sub:volumelimiting}) to calculate completeness.  We take the $z<1.0$ flux-limited sample to fit redshift distribution models (cf.~\S\ref{sub:overdensities}) and then restrict ourselves to $z\le1$ sample for all further analysis.
% ($S/N \sim 50$ {\bf ?} )
% \rachel{Our catalog has the more up-to-date Ilbert et al. photo-$z$,
%   not the older Mobasher ones.  Need to fix citations. Also, we care
%   about the photo-$z$ accuracy beyond 22.5, so it's important to give
%   some information about it to the depth that we actually use.  Finally, I
%   recommend against mentioning the $S/N$ because the calculation is
%   complicated by the correlated noise, so most people use use
%   magnitude instead of $S/N$.}

@@

%\rachel{I thought we were only going up to $z=0.85$ but here you say $1$?}
%For our sample of galaxies, volume-limited upto $z=1$ by imposing an $M_I$ cut, we fit parametric models to the histogram of photometric redshifts in order to assign values of overdensity. The figures show chi-squared and gamma functions fitted to the histogram~\citep{Redshift_modelling}.
For our (flux-limited) sample of galaxies, up to $z=1.0$, we fit parametric models to the histogram of photometric redshift in order to assign values of overdensity. Figures show Chi-squared distribution given by
\begin{equation}
 p_1(z) \sim z^{a-1}\exp({-bz})
\end{equation}
and the function given by
\begin{equation}
 p_2(z) \sim z^2\exp{\left(-\left(\frac{z}{z_0}\right)^{1.5}\right)}
\end{equation}
that was first presented by~\cite{Redshift_modelling} as fits to the
redshift histograms. The normalization constants depend not only on the parameters but also on the lower and the upper limit of the redshifts considered. \rachel{(To avoid ambiguity, you should use avoid
  using the same symbol in both equations.  For example you could turn
  the $b$'s into $b_1$ and $b_2$.  Also, the normalization factors out
  front do not matter - they are not something that you fit for.  I
  would say $p(z)\propto$\dots to avoid 
  the need for a normalization for which you are not actually fitting.)} Here $a,b$ and $z_0$ are free parameters that are to be determined.
%\rachel{You cannot expect people to look these up.  Give them equations in which you define $p(z)$ for each case, with labels like $p_1(z)$ and $p_2(z)$.}
For low $z$, the volume is too small to rely the overdensity values from our model fits and hence the fit is made for $z \ge 0.3$. Our binning width, $\Delta z$ must be small enough so as to be able to identify localized overdensities/underdensities but large enough to not let our conclusions be affected by the errors in photometric redshift. 
We choose our bins to be $0.05$ wide starting from $z=0.3$. 
%\rachel{Were you going to use other fitting functions as a test of the method?  If so, you should introduce them here.}
